Crawler and Inverted Index in Java

### 2023-11-05 latexJava/paperJava.tex
Improve query engine

The "Crawler" module consists of a set of interconnected classes, each contributing to the execution of this complex task. This detailed description sheds light on how these classes work together in the process of downloading and handling book content.
The classes mentioned work as follows:
\begin{itemize}
\item
The \texttt{ContentExtractor} class plays a fundamental role in the process by fetching text from specific books hosted on Gutenberg.org. It is capable of extracting textual data from the site using HTTP requests. To initiate the process, it requires a unique book identifier, and upon successful retrieval, it returns the book's text. This class serves as the initial point of contact with the online library.
\item
The \texttt{FileSystemDatalake} class is responsible for the storage and management of the downloaded textual content. It converts the raw book text into JSON format and stores it in files, with each file named after the respective book's identifier. This class plays a crucial role in creating and maintaining the Datalake directory structure, ensuring organized and efficient data storage.
\item
The \texttt{LibroGutenberg} class is pivotal in the process of extracting meaningful information from the downloaded book text. It utilizes regular expressions to search for and identify various attributes, such as the book's title, author, publication date, language, and, most importantly, the book's actual textual content. This class ensures the structured extraction of metadata and book text.
\item
The \texttt{TimerAPI} class provides an interface for configuring essential parameters related to the book retrieval process. It allows for the adjustment of the execution period, which determines how frequently the system fetches new books. Additionally, it enables users to specify the number of books to download per minute and set a maximum limit for the number of books to retrieve. This class is accessible through an HTTP interface, making it a valuable tool for process customization.
\item
The \texttt{Controller} class serves as the orchestrator of the entire process. It initiates a timer that cyclically triggers the execution of operations for downloading and saving book texts. During this continuous process, it leverages the functionality of the \texttt{ContentExtractor}, \texttt{FileSystemDatalake}, and \texttt{LibroGutenberg} classes. By doing so, it ensures that books are fetched, processed, and stored systematically.
\end{itemize}
Finally The main \texttt{Main} class initializes the entire system. It sets the port for the system, initializes the Spark server, and passes the location of the Datalake directory to the \texttt{Controller} class.

@@

\begin{itemize}
\item
The \texttt{Controller} class serves as the controller in the Query Engine module. It is responsible for initializing and running a server that handles client requests. The \texttt{Controller} class invokes the \texttt{startServer} method of the \texttt{SparkWebService} object.

\item
The \texttt{SparkWebService} class utilizes the Spark library to launch an HTTP server. This server listens on a specified port and handles HTTP requests, particularly GET requests. It provides a single main query, \texttt{/v1/search}, allowing users to search for documents based on keywords.

\item
The \texttt{SqliteReader} class is responsible for communication with the SQLite database, which stores information about keyword indexes within documents. When the server receives a request with a keyword, the \texttt{SqliteReader} extracts information about the documents containing that keyword from the database.

@@

The \texttt{Main} class contains the \texttt{main} function, which serves as the entry point for the Query Engine module. It primarily initializes a \texttt{Controller} object and starts the API server.

The collaboration among these classes is as follows: The Spark server listens for search requests and, upon receiving a query, forwards it to the \texttt{SqliteReader}. The \texttt{SqliteReader} communicates with the SQLite database to retrieve documents containing the specified keyword. The results are processed and returned to the client in JSON format via the Spark server. This allows users to search for documents based on keywords and receive results efficiently.

@@

In the future, the new file datamart could be improved further to be faster using all sorts of different caching techniques to reduce the number of IO operations.

>>>>

The "Crawler" module consists of a set of interconnected classes, each contributing to the execution of this complex task. This detailed description sheds light on how these classes work together in the process of downloading and handling book content.
The classes mentioned work as follows:
\begin{itemize}
\item
The \texttt{ContentExtractor} class plays a fundamental role in the process by fetching text from specific books hosted on Gutenberg.org. It is capable of extracting textual data from the site using HTTP requests. To initiate the process, it requires a unique book identifier, and upon successful retrieval, it returns the book's text. This class serves as the initial point of contact with the online library.
\item
The \texttt{FileSystemDatalake} class is responsible for the storage and management of the downloaded textual content. It converts the raw book text into JSON format and stores it in files, with each file named after the respective book's identifier. This class plays a crucial role in creating and maintaining the Datalake directory structure, ensuring organized and efficient data storage.
\item
The \texttt{DocumentParser} class is pivotal in the process of extracting meaningful information from the downloaded book text. It utilizes regular expressions to search for and identify various attributes, such as the book's title, author, publication date, language, and, most importantly, the book's actual textual content. This class ensures the structured extraction of metadata and book text.
\item
The \texttt{TimerAPI} class provides an interface for configuring essential parameters related to the book retrieval process. It allows for the adjustment of the execution period, which determines how frequently the system fetches new books. Additionally, it enables users to specify the number of books to download per minute and set a maximum limit for the number of books to retrieve. This class is accessible through an HTTP interface, making it a valuable tool for process customization.
\item
The \texttt{Controller} class serves as the orchestrator of the entire process. It initiates a timer that cyclically triggers the execution of operations for downloading and saving book texts. During this continuous process, it leverages the functionality of the \texttt{ContentExtractor}, \texttt{FileSystemDatalake}, and \texttt{LibroGutenberg} classes. By doing so, it ensures that books are fetched, processed, and stored systematically.
\end{itemize}
Finally The main \texttt{Main} class initializes the entire system. It sets the port for the system, initializes the Spark server, and passes the location of the Datalake directory to the \texttt{Controller} class.

@@

\begin{itemize}
\item
The \texttt{SparkWebService} class utilizes the Spark library to launch an HTTP server. This server listens on a specified port and handles HTTP requests. It provides two endpoints,
\begin{itemize}
	\item \texttt{/v1/search}, allowing users to search for documents based on keywords, with a pagination feature for retrieving results in batches.
	\item \texttt{/v1/document/:id}, allowing users to get a particular document.
\end{itemize}
\item

@@

The \texttt{Main} class contains the \texttt{main} function, which serves as the entry point for the Query Engine module.
It accepts two command-line arguments: the path to the \texttt{datalake}, which is where the documents themselves are stored, and to the datamart \texttt{datamart}, which is the index of all the documents.
It then initializes the \texttt{SparkWebService} class and makes it listen for HTTP requests.

@@

In the future, the new file datamart could be improved further to be faster using all sorts of different caching techniques to reduce the number of IO operations.
Aditionally, various parts of the indexer could be improved further by having its own cache and flush features added, so that it doesn't flush all the indexed documents to the datamart one by one.
